Technical Report

### 2018-02-26 fully-abstract-comp/technical-report.tex
Fix some typos.
Minor tweaks, remove outdated comment.
Add comment.
Add date to comment.
Fix sentence.

\[
  \memSatStack{\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      W_\var{stack} = \pi_2(W) \wedge \\
      \stk = (\opc_0,\ms_0), \dots (\opc_m,\ms_m) \wedge \\
      \exists R_\ms : \dom(\activeReg{W_\var{stack}}) \fun \MemSeg \times \SealableCaps \times \MemSeg \ldotp \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{W_\var{stack}})} \pi_3(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{W_\var{stack}}) \fun \World \ldotp \\
      \qquad W = \bigoplus_{r \in \dom(\activeReg{W_\var{stack}})} R_W(r) \wedge \\
      \qquad \forall r \in \dom(\activeReg{W_\var{stack}}), n' < n \ldotp \\
      \qquad \quad \npair[n']{(\pi_1(R_\ms(r)),\pi_3(R_\ms(r))} \in W_\var{stack}(r).H \; W_\var{stack}(r).s \; \xi^{-1}(R_W(r)) \\
      \qquad \quad \pi_2(R_\ms(r)) = W_\var{stack}(r).\opc \wedge\\
      \qquad \quad \exists i \ldotp \opc_i = W_\var{stack}(r).\opc \wedge \ms_i = \pi_1 (R_\ms(r))
    \end{array}
  \right.
\]

\[
  \memSatFStack{ms_\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      W_\var{stack} = \pi_3(W) \wedge \\
      \exists R_\ms : \dom(\activeReg{W_\var{stack}}) \fun \MemSeg \times \MemSeg \wedge \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{W_\var{stack}})} \pi_2(R_\ms(r)) \wedge \\
      \quad \ms_\stk = \biguplus_{r \in \dom(\activeReg{W_\var{stack}})} \pi_1(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{W_\var{stack}}) \fun \World\ldotp\\
      \qquad W = \oplus_{r \in \activeReg{W_\var{stack}}} R_W(r) \wedge\\
      \qquad \forall r \in \activeReg{W_\var{stack}}, n' < n \ldotp \\
      \qquad \quad \npair[n']{R_\ms(r)} \in  W_\var{stack}(r).H \; W_\var{stack}(r).s \; \xi^{-1}(R_W(r))
    \end{array}
  \right.
\]

\[
  \memSatHeap{ms,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      W_\var{heap} = \pi_1(W) \wedge \\
      \exists R_\ms : \dom(\activeReg{W_\var{heap}}) \fun \MemSeg \times \MemSeg \wedge \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{W_\var{heap}})} \pi_2(R_\ms(r)) \wedge \\
      \quad \ms = \biguplus_{r \in \dom(\activeReg{W_\var{heap}})} \pi_1(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{W_\var{heap}}) \fun \World\ldotp\\
      \qquad W = \oplus_{r \in \activeReg{W_\var{heap}}} R_W(r) \wedge\\
      \qquad \forall r \in \activeReg{W_\var{heap}}, n' < n \ldotp \\
      \qquad \quad \npair[n']{R_\ms(r)} \in  W_\var{heap}(r).H \; W_\var{stack}(r).s \; \xi^{-1}(R_W(r))
    \end{array}
  \right.
\]
}

@@

\subsection{Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
% \[
%   \lre(W) = \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
%     \begin{array}{l}
%       \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
%       \quad \forall W_\lrr, W_\lrm \ldotp \\
%       \qquad\npair[n']{[\stpair[.]{v_{c,S}}{v_{c,T}},\stpair[.]{v_{d,T}}{v_{d,S}}]} \in \lrp(W) \wedge \\
%       \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
%       \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \wedge\\
%       \qquad W_{\var{new}} = W \oplus W_\lrr \oplus W_\lrm \\
%       \qquad\Rightarrow\\
%       \qquad\npair[n']{\left(\array{l}\src{(\ms_S,\reg_S\updReg{\pcreg,\rdata}{v_{c,S},v_{d,S}},\stk, \ms_\stk)},\\
%                                           (\ms_T,\reg_T\updReg{\pcreg,\rdata}{v_{c,T},v_{d,T}})
%                        \endarray\right)}
%       \in \lro
%     \end{array}
%     \right\}
% \]
% \lau{24-10-2017: Dominique, I do not see how the splitting of worlds is going to work out. I can see how it will enforce linearity, but if you give a "spatial" region (the kind of region that is only allowed to go to one part of a split) to the $\lrr$-relation, then the memory satisfaction does not have it, and it cannot find a memory segment for this part. In other words, the memory satisfaction will not be able to find a concrete memory segment for segments governed by a linear capability in the register file. Maybe the memory satisfaction should have all of the parts, so it can represent them (but also limit what linear capabilities can be used).}
% \dominique{18-1-2018: Lau, I suppose the above has been answered verbally already during one of the previous skype calls, but for reference, this is what the spatial vs spatial\_owned distinction is intended to solve: the world will contain spatial regions for such memory segments, but not spatial\_owned ones, so the memory satisfaction will require the memory to be present but not allow it to be addressed.}

@@

    \end{array}
  \]
\end{theorem}

@@

\clearpage
\section{Back translation}
The back translation is an embedding of source language into .

>>>>

\[
  \memSatStack{\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      W_\var{stack} = \pwpriv \wedge \\
      \stk = (\opc_0,\ms_0), \dots (\opc_m,\ms_m) \wedge \\
      \exists R_\ms : \dom(\activeReg{W_\var{stack}}) \fun \MemSeg \times \SealableCaps \times \MemSeg \ldotp \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{W_\var{stack}})} \pi_3(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{W_\var{stack}}) \fun \World \ldotp \\
      \qquad W = \bigoplus_{r \in \dom(\activeReg{W_\var{stack}})} R_W(r) \wedge \\
      \qquad \forall r \in \dom(\activeReg{W_\var{stack}}), n' < n \ldotp \\
      \qquad \quad \npair[n']{(\pi_1(R_\ms(r)),\pi_3(R_\ms(r))} \in W_\var{stack}(r).H \; W_\var{stack}(r).s \; \xi^{-1}(R_W(r)) \\
      \qquad \quad \pi_2(R_\ms(r)) = W_\var{stack}(r).\opc \wedge\\
      \qquad \quad \exists i \ldotp \opc_i = W_\var{stack}(r).\opc \wedge \ms_i = \pi_1 (R_\ms(r))
    \end{array}
  \right.
\]

\[
  \memSatFStack{ms_\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      W_\var{stack} = \pwfree \wedge \\
      \exists R_\ms : \dom(\activeReg{W_\var{stack}}) \fun \MemSeg \times \MemSeg \wedge \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{W_\var{stack}})} \pi_2(R_\ms(r)) \wedge \\
      \quad \ms_\stk = \biguplus_{r \in \dom(\activeReg{W_\var{stack}})} \pi_1(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{W_\var{stack}}) \fun \World\ldotp\\
      \qquad W = \oplus_{r \in \dom(\activeReg{W_\var{stack}})} R_W(r) \wedge\\
      \qquad \forall r \in \dom(\activeReg{W_\var{stack}}), n' < n \ldotp \\
      \qquad \quad \npair[n']{R_\ms(r)} \in  W_\var{stack}(r).H \; W_\var{stack}(r).s \; \xi^{-1}(R_W(r))
    \end{array}
  \right.
\]

\[
  \memSatHeap{ms,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      W_\var{heap} = \pwheap \wedge \\
      \exists R_\ms : \dom(\activeReg{W_\var{heap}}) \fun \MemSeg \times \MemSeg \wedge \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{W_\var{heap}})} \pi_2(R_\ms(r)) \wedge \\
      \quad \ms = \biguplus_{r \in \dom(\activeReg{W_\var{heap}})} \pi_1(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{W_\var{heap}}) \fun \World\ldotp\\
      \qquad W = \oplus_{r \in \activeReg{W_\var{heap}}} R_W(r) \wedge\\
      \qquad \forall r \in \activeReg{W_\var{heap}}, n' < n \ldotp \\
      \qquad \quad \npair[n']{R_\ms(r)} \in  W_\var{heap}(r).H \; W_\var{stack}(r).s \; \xi^{-1}(R_W(r))
    \end{array}
  \right.
\]
}

@@

\subsection{Relation}
% \lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
% \[
%   \lre(W) = \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
%     \begin{array}{l}
%       \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
%       \quad \forall W_\lrr, W_\lrm \ldotp \\
%       \qquad\npair[n']{[\stpair[.]{v_{c,S}}{v_{c,T}},\stpair[.]{v_{d,T}}{v_{d,S}}]} \in \lrp(W) \wedge \\
%       \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
%       \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \wedge\\
%       \qquad W_{\var{new}} = W \oplus W_\lrr \oplus W_\lrm \\
%       \qquad\Rightarrow\\
%       \qquad\npair[n']{\left(\array{l}\src{(\ms_S,\reg_S\updReg{\pcreg,\rdata}{v_{c,S},v_{d,S}},\stk, \ms_\stk)},\\
%                                           (\ms_T,\reg_T\updReg{\pcreg,\rdata}{v_{c,T},v_{d,T}})
%                        \endarray\right)}
%       \in \lro
%     \end{array}
%     \right\}
% \]
% \lau{24-10-2017: Dominique, I do not see how the splitting of worlds is going to work out. I can see how it will enforce linearity, but if you give a "spatial" region (the kind of region that is only allowed to go to one part of a split) to the $\lrr$-relation, then the memory satisfaction does not have it, and it cannot find a memory segment for this part. In other words, the memory satisfaction will not be able to find a concrete memory segment for segments governed by a linear capability in the register file. Maybe the memory satisfaction should have all of the parts, so it can represent them (but also limit what linear capabilities can be used).}
% \dominique{18-1-2018: Lau, I suppose the above has been answered verbally already during one of the previous skype calls, but for reference, this is what the spatial vs spatial\_owned distinction is intended to solve: the world will contain spatial regions for such memory segments, but not spatial\_owned ones, so the memory satisfaction will require the memory to be present but not allow it to be addressed.}

@@

    \end{array}
  \]
  \dominique{26-2-2018: $\readCond{\lin,W}$ and $\xReadCond{\lin,W}$ seem contradictory. I suspect the former needs to go?}
\end{theorem}

@@

\clearpage
\section{Back translation}
The back translation is an embedding of the target language into the source language.
